\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}

### 2019-10-29 paper.tex
Eliminate the listing of keywords to 4 to fit guidelines
WIP

\begin{IEEEkeywords}
    streaming data, data integrity, data marketplace, decentralization, blockchain
\end{IEEEkeywords}

@@

>>>>

\begin{IEEEkeywords}
    streaming data, data integrity, data marketplace, decentralization
\end{IEEEkeywords}

@@

\section{Results}
Mask Authenticated Messaging (MAM) is the most important component to ensure the data integrity and privacy in our architecture, and it is C library developed by IOTA Foundation.
